\section{Introduction}

\subsection{Container and Linux Kernel}

The container techniche is a secondary product of the operating system in the past 20 years.
The FreeBSD develops `Jails' in 1999, and the Solaris develops `Zones' in 2004.
Linux also took this idea into the Linux kernel, which is named cgroups (2007),
the namespace (2002), the capabilities (2003), and seccomp (2005). However, why the Linux breaks this
technology into many parts? This is because they had discussed:
``Why Should a System Administrator Upgrade?" in 2001.
%\footnote{\url{https://www.informit.com/articles/article.aspx?p=20667}}.
The Linux kernel almost entered the development path of ``upgrade for demand" like
Microsoft Windows, and deviated from the original path of "providing a mechanism
but not a strategy" of the original Linux kernel.

While Linux were spreading in various server or distributed system, the
Linux community got more pull requests to solved the scalability and virtualization
issues \cite{267148}. However, they avoided confusion caused by multiple meanings of
the term `container' in the Linux kernel context. In kernel version 2.6.24 (2007)
\footnote{\url{https://lwn.net/Articles/256389/}},
control groups functionality was merged into the mainline,
which is designed for an administrator (or administrative daemon) to organize processes
into hierarchies of containers; each hierarchy is managed by a subsystem. Moreover, the
cgroups was rewrote into cgroups-v2 in Linux kernel 4.5 (2015).

Containers offers ``build once, run anywhere." Docker does this by bundling
applications with all their dependencies into one package and isolating applications
from the rest of the machine on which they're running. Therefore, this research
is based on docker container to propose a scheme of healthcare data exchange system's
security.

\subsection{Fast Healthcare Interoperability Resources (FHIR)}
FHIR is a standard for healthcare data exchange. The FHIR standard will be used in
Taiwan in the near future. FHIR will be used to provide PHR (Personal Healthcare Records)
in Taiwan. Therefore, we choose the most popular standard "FHIR" for the target of
the healthcare data exchange system.

This paper will take IBM FHIR server as an example. 
There are many applications using IBM's FHIR server as the base component of the EHR
(Electronic Health Records) system to communicate with the other various databases.
Take it for example that the NextCloud's EHR service, Taipei Veterans General Hospital,
and AWS Cloud are using the FHIR server in a container for subroutine service.
Many people caring about their privacy issues distrust the FAAMG (Facebook,
Amazon, Apple, Microsoft, Google), so they are using NextCloud to keep their privacy
on their own. Therefore, they are eager to have a secure EHR system for their
PHR
\footnote{\href{https://www.youtube.com/watch?v=AAP4N3KyLmM}{Richard Stallman talks about IoT}}.

The benefits of providing IBM FHIR container security in our study are providing
secure protection testing, methods, and performance evaluation for FHIR services provided by
a well-known international company (IBM). This research will provide an important reference for
commercial projects for the health information exchange system practiced by medical
institutions in Taiwan.
